---
title: "Progress Report"
author: "infoDemocracy"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(readr)
library(dplyr)
library(knitr)
library(leebunce)
library(lubridate)
library(ggplot2)

load("../../Output/info_democracy.Rdata")

```

This report summarises progress made on researching and coding donors.

# 1. Coding progress

This table summaries the progress made in researching individuals and organisations in the donor tables.

## 1.1 Researched

```{r}
table <- info_democracy %>% 
  summarise(`Total number` = n()  %>% format(big.mark = ","),
            `Total value` = sum(dntn_value) %>% format(big.mark = ","),
            `Researched number` = sum(x_researched) %>% format(big.mark = ","),
            `Number %` = percent(sum(x_researched)/n()),
            `Researched value` = sum(dntn_value[x_researched]) %>% format(big.mark = ","),
            `Value %` = percent(sum(dntn_value[x_researched]) / sum(dntn_value)))

kable(table, align = "c")
rm(table)
```

## 1.2 Coded

```{r}
table <- info_democracy %>% 
  summarise(`Total number` = n()  %>% format(big.mark = ","),
            `Total value` = sum(dntn_value) %>% format(big.mark = ","),
            `Coded number` = sum(x_coded) %>% format(big.mark = ","),
            `Number %` = percent(sum(x_coded)/n()),
            `Coded value` = sum(dntn_value[x_coded]) %>% format(big.mark = ","),
            `Value %` = percent(sum(dntn_value[x_coded]) / sum(dntn_value)))

kable(table, align = "c")
rm(table)
```

# 2. Coded by year

The chart below shows the total value of donations per year, anlong with the proportion of that value that has been coded.

```{r warning=FALSE}
info_democracy %>% 
  filter(x_donation_year >= 2001) %>% 
  group_by(x_donation_year, Coded = x_coded) %>% 
  summarise(total = sum(dntn_value)) %>% 
  ggplot(aes(x_donation_year, total, fill = Coded)) + 
  geom_bar(stat='identity') +
  labs(title = 'Total value and proportion coded by year',
       x = 'Year',
       y = 'Total value (£)')
```

# 3. Not coded by recipient

## 3.1 Uncoded donations by recipient
This table looks at the uncoded donations by recipient. Only the top 6 biggest recipients are shown.

```{r}
info_democracy %>% 
  filter(interest_code == 'ZZZZZ') %>% 
  group_by(Recipient = dntn_regulated_entity_name) %>% 
  summarise(n = n(),
         Total = sum(dntn_value)) %>% 
  arrange(desc(Total)) %>% 
  mutate(Percent = percent(Total/sum(Total)),
         Total = format(Total, big.mark = ",")) %>% 
  head() %>% 
  kable(align = c('l', 'c', 'c', 'c'))
```

## 3.2 Percentage coded for key recipients

For recipients who have received over £10 million, this table gives the percentage of donations that have been coded.

```{r}
info_democracy %>% 
  group_by(Recipient = dntn_regulated_entity_name) %>% 
  summarise(Donations = n(),
            Value = sum(dntn_value),
            `Value coded` = sum(ifelse(x_coded == T, dntn_value, 0)),
            `Percent value coded` = percent(sum(ifelse(x_coded == T, dntn_value, 0))/sum(dntn_value))) %>% 
  filter(Value >= 10000000) %>% 
  arrange(desc(Value)) %>% 
  mutate(Donations = format(Donations, big.mark = ','),
         Value = format(Value, big.mark = ','),
         `Value coded` = format(`Value coded`, big.mark = ',')) %>% 
  kable(align = c('l', 'c', 'c', 'c', 'c'))



```


# 4. Sector

```{r}

info_democracy %>% 
  filter(level_1_description != 'Not yet coded') %>% 
  group_by(level_1_short) %>% 
  summarise(Total = sum(dntn_value)) %>% 
  ggplot(aes(level_1_short, Total)) +
  geom_bar(stat = 'identity', fill = 'navyblue') +
  coord_flip()

```

